IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-16 paper/conclusion.tex
Pass conclusions

In this paper, we argued that when designing a coarse-grained IFC
system, it is better to start with a fully isolated, multi-task system
and work one's way back to the model of a single language.  We showed
how to prove systems designed this way can be proved noninterferent,
without needing to rely on details of the target language, and
we provided conditions on how to securely refine our formal semantics to
consider optimizations required in practice.  We connected our semantics
to existing IFC implementations for JavaScript and Haskell, and proposed
an IFC system for C using hardware isolation.
By systematically applying ideas from IFC in operating systems to programming languages,
we hope to have elucidated some of the core design principles of coarse-grained,
dynamic IFC systems.

>>>>

In this paper, we argued that when designing a coarse-grained IFC
system, it is better to start with a fully isolated, multi-task system
and work one's way back to the model of a single IFC-aware language.  We showed
a formal framework capable to prove secure (i.e. non-interferent) systems designed this way,
without needing to rely on details of the target language.
%, and
%we provided conditions on how to securely refine our formal semantics to
%consider optimizations required in practice.
We provide soundness guarantees for the COWL's JavaScript monitor by simply
connecting our framework to that implementation.
%% to two IFC implementations for JavaScript based on this formalism,
%% explained how our methodology improved an exiting IFC system for Haskell,
%% and proposed
%% an IFC system for C using hardware isolation.
By systematically applying ideas from IFC in operating systems to programming languages,
we hope to have elucidated some of the core design principles of coarse-grained,
dynamic IFC systems.
